Deciding to Disclose

### 2015-11-10 acronyms.tex
acronyms to own file

\documentclass[graybox]{svmult}
\usepackage[hyperfootnotes=false]{hyperref}
\hypersetup{bookmarksdepth=3}

\usepackage{mathptmx}       \usepackage{helvet}         \usepackage{courier}        \usepackage{type1cm}                                    \usepackage{makeidx}         \usepackage{graphicx}                                     \usepackage{multicol}        \usepackage[bottom]{footmisc} \usepackage{adjustbox}
 \usepackage{multirow}
 \usepackage{algorithm}
 \usepackage{algpseudocode}
 \usepackage{ifthen}
 \usepackage{csquotes}
 \usepackage{amsmath}

\usepackage{comment}
 \usepackage{natbib}
 \setcitestyle{numbers,square}
 \usepackage[subrefformat=parens,labelformat=simple,caption=false,labelfont={bf}]{subfig}
 \usepackage[nolist,smaller]{acronym}
\allowdisplaybreaks
\makeindex

\begin{document}
\begin{acronym}[ALSPAC]
  \acro{FAS}{Foetal Alcohol Syndrome}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{PT}{Prospect Theory}
  \acro{NICE}{the National Institute for Health and Care Excellence}
  \acro{IAPT}{Improving Access to Psychological Therapies}
  \acro{CMACE}{Centre for Maternal and Child Enquiries}
  \acroindefinite{CMACE}{the}{the}
  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
  \acroindefinite{RCOG}{the}{the}
  \acro{AML}{acute myeloid leukemia}
  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
  \acro{PND}{Postnatal Depression}
  \acro{RCT}{randomised control trial}
  \acro{WHO}{the World Health Organisation}
  \acro{ESS}{Evolutionarily Stable Strategy}
  \acrodefplural{ESS}[ESS]{Evolutionarily Stable Strategies}
  \acro{MCMC}{Markov chain monte carlo methods}
  \acro{DU}{Discounted Utility}
  \acro{AIC}{Akaike information criterion}
  \acro{ANOVA}{analysis of variance}
  \acro{ALSPAC}{the Avon Longitudinal Study of Parents and Children}
  \acro{GEM}{Gaussian Emulation Machine}
  \acrodefplural{GEM}{Gaussian Emulation Machines}
  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
  \acro{JIT}{Just-in-time}
  \acro{ABM}{Agent Based Modelling}
  \acro{ABMs}{Agent Based Models}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{FFH}{Fast and Frugal Heuristic}
  \acro{OFC}{orbito-frontal cortex}
  \acro{BACCO}{Bayesian Analysis of Computer Code Outputs}
  \acro{IQR}{interquartile range}
\end{acronym}

\title*{Deciding to Disclose}
\subtitle{A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse}

\author{Jonathan Gray, Jakub Bijak, and Seth Bullock}
\institute{Jonathan Gray \at University of Southampton, Southampton, United Kingdom \email{j.gray@soton.ac.uk}
\and Jakub Bijak \at University of Southampton, Southampton, United Kingdom \email{j.bijak@soton.ac.uk}
\and Seth Bullock \at University of Southampton, Southampton, United Kingdom \email{sgb@ecs.soton.ac.uk}}

\maketitle

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax

\section*{Abstract}

We draw together methodologies from game theory, agent based modelling, decision theory, and uncertainty analysis to explore the process of decision making in the context of pregnant women disclosing their drinking behaviour to their midwives.

We employ a game theoretic framework to define a signalling game. The game represents a scenario where pregnant women decide the extent to which they disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether to refer their patients for costly specialist treatment. This game is then recast as two games played against \enquote{nature}, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
Four decision rules are explored - a lexicographic heuristic which considers only the link between moves and payoffs, a Bayesian risk minimisation agent that uses the same information, a more complex Bayesian risk minimiser with full access to the structure of the decision problem, and a \ac{CPT} rule.

In simulation, we recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of social learning within agent groups.
Finally a global sensitivity analysis using \acp{GEM} is conducted, to compare the response surfaces of the different decision rules in the game. \acresetall

\section{Introduction}
\label{sec:intro}

The case in favour of \ac{ABM} as a general analytical approach has been made numerously, and elegantly (e.g. \cite{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others). As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, reflecting the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}. To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, one player (the signaller), has some piece of information that is known only to them which affects the outcome of the game for both players. The signaller has a choice as to what they tell the other player about this hidden information, and the responding player as to what they believe the information to be.} \citep{Kreps1987} with a basic form of intragroup social learning. Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

This exercise is framed in the context of disclosure decisions, taking drinking patterns in pregnant women as a motivating example. Alcohol consumption in the antenatal period is a significant issue in itself, although there is not a clear consensus on associated risk. In terms of official guidance in the UK, \ac{NICE} acknowledge that evidence of harm to the fetus is less than conclusive, but advise not drinking at all, or significant moderation \citep{NICE2010a}, with similar advice from the UK \cite{DepartmentofHealth2008}.

Turning more specifically to disclosure of alcohol use by women to healthcare professionals during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}. The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking. The simulation model described in this paper is able to replicate both qualitative trends, i.e. an increase in disclosure over appointments, and more honest behaviour by moderate as compared to heavier drinkers.

The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in domains where the process is obscured, here both because of the interest in concealment, and obvious ethical concerns. With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{epstein2008}, rather than a machine for predicting.

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions. But equilibrium is the sine qua non of game theory, which is concerned with the stable outcome of an infinite contest of second guesses.
We wish to see the system in motion rather than just at rest, even if it does eventually settle to some stable point. Instead, we choose to focus instead on the behavioural processes driving a system in motion, a system out of equilibrium, to understand how these processes interact with the movement.
Introducing decision theory takes a step down the ladder of abstraction from the mental chess of game theory. Dealing instead in the mechanics of decision making, and the calculus of choice, allows us to explore not only paths that arrive at the destinations we might consider in game theory, but also avenues not accessible where we constrain ourselves to a sometimes implausible degree of rationality.

This does not preclude a strategic dimension, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the decision problem. In addition, rules are agnostic as to the source of information, suggesting room for multi-stage processes - for example, a game theoretic, model of the opponent's mind, approach could act as an information source for a decision rule.  As a corollary, the decision problem agents attempt to answer can change, allowing behaviour in novel problems to be informed by beliefs derived under other conditions. This is also indicative of the broader benefits to \ac{ABM} as an approach. Embedding these abstract rules in a simulated environment allows for mechanics which cannot be readily explored using purely analytic, or predictive approaches, for example, the social learning dynamic of the disclosure game model.

While there is no universal theory of human behaviour to sit at the centre of \ac{ABM} as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible. Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}. Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings. In addition, a single decision rule represents a parsimonious alternative to numerous case specific production rules.

Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is process, and decision making. Taking a balance between models focused on replication of low level neurological mechanics, and those with a higher level emphasis where individual behaviours are abstracted away, yields a computationally tractable approach. Despite the relative simplicity, it nonetheless captures some of the nuance and sophistication of human decisions.

The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}). 
\section{Disclosure Game Model}
\label{sec:model}

In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with a schedule of simulation provided in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and translating this to a simulation model. We then outline four possible decision rules, and as an example of additional flexibility of process models and simulation in contrast to purely predictive or analytical approaches, extend the model to allow a simple form of social learning.

\subsection{Modelling Approach}
\label{sec:model_design}

To model a scenario, we take the approach of first creating a formal game to represent it, capturing the key features as far as possible in the structure of that game. This game is in essence a conjecture about the real data generating process, which can be played out in simulation.

The appropriate game representative of the scenario of interest, which captures the desired strategic dynamics may not be immediately obvious. We suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.

Transitioning from the resulting game, to a set of decision problems is a relatively simple task. We treat the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance. As with the game, the decision problem representation admits a degree of variation, and may need to be adjusted to reflect the decision rules that will be used.

These decision problems may then form the basis of an agent model, where agents use learning, and decision rules to play out the game. Simulation can then support features which are not readily representable within an analytic framework, for example, populations of heterogeneous players, individual and social learning, or network effects. In addition, the ability to observe the system in a state of flux rather than at equilibrium is desirable, since even where a social system reaches a stable state, the process by which we arrive at it is significant.

\subsection{Scenario}
\label{sec:scenario}

Typically in the UK, women have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care. In the UK, and unlike most healthcare contexts, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, followed by subsequent action if a concern is raised is at the discretion of the midwife. This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team. On alcohol consumption, policy regarding how to determine the level of consumption is at the time of writing generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE. This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test for alcohol misuse intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.

Beyond the \enquote{booking} appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted. In either case, once a concern has been raised the midwife must respond clinically, and inevitably personally, to the information.

In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient. However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{NICE2010,Radcliffe2011}.

\subsection{Disclosure Game}
\label{sub:the_game}

In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals. We also impose a discretisation on the continuum of alcohol use, and use three types of behaviour - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy. Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.

Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental. The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.

At the end of a game, each player receives a payoff dependent on the actions and types of both players. Because both women and midwives have an interest in the outcome of the pregnancy, and would prefer a healthy baby, the payoff has a common interest component. Hence, both players receive a payoff based on the outcome of pregnancy, but women bear a social cost dependent on the signal they sent and the midwife's reaction to it. Similarly, midwives pay a cost if they refer to a specialist, mirroring the organisational cost of non-routine care. Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.

\begin{table}
\caption{Payoff matrices}
\label{tab:Payoff-matrix}
\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline
\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Harsh & -2 & -1 & 0\tabularnewline
\cline{2-5} 
 & Moderate & -1 & 0 & 0\tabularnewline
\cline{2-5} 
 & Non & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

}\qquad
\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & 10 & 10 & 10\tabularnewline
\cline{2-5} 
 & Don't refer & -2 & -1 & 10\tabularnewline
\hline 
\end{tabular}

}

\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9 & -9 & -9 \tabularnewline
\cline{2-5} 
 & Don't refer & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

}
\end{table}

As an example, consider the challenge faced by an agent of the heavy drinking type. In order to get the best health outcome, they must be referred and would ideally achieve this without paying any social cost at all. The best move depends on the type, and beliefs of the midwife. For example, a particularly unlucky scenario might be for the midwife to not only be of a harshly judgemental disposition, but to believe that no women really need to be referred (i.e. that all women are light drinkers). Even a relatively weak belief in this possibility can make the honest signal look like an unwarranted risk.

To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives. Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
Additionally define two utility functions - 
\begin{equation}
u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}
\end{equation} 
\begin{equation}
u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife. Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.

As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)). They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.

Midwives play for \(r_{m}\) rounds (\(r_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e. if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives. 
Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

\subsection{Social Learning}
\label{sub:info_sharing}

In reality, learning is not exclusively from personal experience, and social learning plays an important role. This social dynamic fits naturally into an agent framework, but is difficult to address without using an approach concerned with process, so we take advantage of this to show a na{\"\i}ve take on it here.

In the disclosure game model, this takes the form of having each agent recount their play history to their colleagues with some probability \(q\). Individuals then incorporate shared information into their beliefs using weighted updates, e.g. for a midwife a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e. \(n_{j} = n_{j} + w\)).
Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.} Accounts are shared with some probability, to all fellow players. For example, a heavy drinker finishes play having claimed to be a light drinker, without ever being referred, and their account is selected to be shared with some probability $q_{w}$.

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently. The simple payoff based rule relies on a belief structure relating actions directly to rewards which is essentially model free. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

A payoff based agent, who is a light drinker, hears the account of the heavy drinker. They take the account as literally happening to them, and update their beliefs to include the possibility that there is a negative outcome attached to claiming to be a light drinker.

By contrast, representing the problem in terms of the probabilities of the individual lotteries imposes a model that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes. This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.

Returning to our example, a light drinker using this decision rule would follow the account through from their position in the game tree, correctly inferring that the outcome in their case would be positive. \subsection{Agent Models}
\label{sub:the_agents}

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

Agents have perfect recall, midwives recognise women if they repeatedly encounter them, making use of new information for retrospective updates. However, all four agent models make decisions `as-if' they were always facing a new \enquote{opponent}.

A simplifying assumption is made that all midwives have just qualified after receiving identical training. As a result, they have homogeneous beliefs about  women and assume to some extent that they are honest.
Women have heterogeneous beliefs, which correspond to experiencing \(k\) randomly chosen paths through the game, and following each path at least once.

\subsubsection{Lexicographic Heuristic}
\label{sub:lexico}

The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.

Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) - i.e. \(s_{w}\) is a choice between simple lotteries. The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).

Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice - \(f(s_{w}, s_{m},\sigma)\). This is resolved by maintaining a separate count for each signal (i.e. \(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm (\ref{alg:lexico}).

\begin{algorithm}
\begin{algorithmic}
\State $n \gets 1, action \gets none$
\While{$action = none$}
\State Calculate the $n$th most common outcome following each action.
\State Sort actions by the value of the $n$th most common outcome.
\If{clear winner} \State $action \gets best$ \EndIf
\State $n \gets n + 1$
\EndWhile
\State \Return action
\end{algorithmic}
\caption{Lexicographic heuristic\label{alg:lexico}}
\end{algorithm}

\subsubsection{Bayesian Payoff}

The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using the Bayes rule, and attempts to choose the action which minimises risk.

Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. 
The distribution is particularly convenient, in that to infer the
probability of a signal implying a payoff is
simply -

\begin{equation}
p(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
\end{equation}

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs. Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\). Hence,
the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.

Agents then choose the strategy $s_{i}$ to minimise risk $R_{i}$, which is simply defined as - 
\begin{equation}
R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m}),
\end{equation}

where $X$ is the set of payoffs the agent has observed to follow $s_{i}$.

\subsubsection{Bayesian Risk Minimisation}

The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known. Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice. This leads to the risk function, minimised with respect to \(s_{w}\) -

\begin{equation}
R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
\end{equation}

so that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.

Midwives reasoning centres on determining the meaning of signals, since given the knowledge of what some signal \(s_{w}\) conveys about the true type of the sender, the payoff for an action is known. As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
\end{equation}

\subsubsection{Descriptive Decision Theory}

The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans. Rather than risk, `prospects', the sequence of payoff-probability pairings in ascending order of payoff, associated with an action  are used as decision criteria. While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations \cite{FoxCPT}. In this instance the Bayesian inference process fills the first stage role.

\ac{CPT} uses transformed probabilities, underweighting small probabilities, and overweighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -

\begin{align}
w^{+}(p) & = \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
w^{-}(p) & = \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
\end{align}

where $p$ is the unweighted probability, and $\gamma$ and $\delta$
are the weights for gain and loss probabilities respectively. Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -

\begin{equation}
v(u_{i})=\begin{cases}
f(u_{i}),& \text{if}\, u_{i}>0\\
0,& \text{if}\, u_{i}=0\\
\lambda g(u_{i}),& \text{if}\, u_{i}<0
\end{cases},
\end{equation}

where,

\begin{equation}
f(u_{i})=\begin{cases}
u_{i}^{\alpha},& \text{if}\,\alpha>0\\
\ln(u_{i}),& \text{if}\,\alpha=0\\
1-(1+u_{i})^{\alpha},& \text{if}\,\alpha<0
\end{cases}
\end{equation}
\begin{equation}
g(u_{i})=\begin{cases}
-(-u_{i})^{\beta},& \text{if}\,\beta>0\\
-\ln(-u_{i}),& \text{if}\,\beta=0\\
(1-u_{i})^{\beta}-1,& \text{if}\,\beta<0
\end{cases},
\end{equation}

and $\alpha$, and $\beta$ are respectively the power of a gain,
and a loss, and \(\lambda\) is a multiplier giving the aversion to loss.

Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where,

\begin{equation}
\pi_{n}^{+}=w^{+}(p_{n})
\end{equation}
\begin{equation}
\pi_{-m}^{-}=w^{-}(p_{-m})
\end{equation}
\begin{equation}
\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
\end{equation}
\begin{equation}
\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
\end{equation}

The \ac{CPT} value of a single outcome prospect \(f=(u_{i};p_{i})\), is $v(u_{i})\pi^{+}(p_{i})$
if $u_{i}\geq0$, and $v(u_{i})\pi^{-}(p_{i})$ otherwise. For any given action the \ac{CPT}
value, \(V\) is the sum of the value of the prospects of that action, as
in the Bayesian risk model, and the agent chooses the option which maximises this quantity. 
\section{Method}
\label{sec:method}

This section provides details of experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \citet{Alvik2006}, and \citet{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.

\subsection{Qualitative Trends}
\label{sub:qt}

Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}). While there has been significant work on determining appropriate parametrisation for the model (e.g. \cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work. For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \acl{ALSPAC} suggest that the reality is far more positive\footnote{95.5\% of women in the sample reported consumption at, or below, \ac{NICE} recommended safe levels.} \citep{Humphriss2013}. The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty. Payoffs were as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.

Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion of the population who were referred. Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.

>>>>

\acro{FAS}{Foetal Alcohol Syndrome}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{PT}{Prospect Theory}
  \acro{NICE}{the National Institute for Health and Care Excellence}
  \acro{IAPT}{Improving Access to Psychological Therapies}
  \acro{CMACE}{Centre for Maternal and Child Enquiries}
  \acroindefinite{CMACE}{the}{the}
  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
  \acroindefinite{RCOG}{the}{the}
  \acro{AML}{acute myeloid leukemia}
  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
  \acro{PND}{Postnatal Depression}
  \acro{RCT}{randomised control trial}
  \acro{WHO}{the World Health Organisation}
  \acro{ESS}{Evolutionarily Stable Strategy}
  \acrodefplural{ESS}[ESS]{Evolutionarily Stable Strategies}
  \acro{MCMC}{Markov chain monte carlo methods}
  \acro{DU}{Discounted Utility}
  \acro{AIC}{Akaike information criterion}
  \acro{ANOVA}{analysis of variance}
  \acro{ALSPAC}{the Avon Longitudinal Study of Parents and Children}
  \acro{GEM}{Gaussian Emulation Machine}
  \acrodefplural{GEM}{Gaussian Emulation Machines}
  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
  \acro{JIT}{Just-in-time}
  \acro{ABM}{Agent Based Modelling}
  \acro{ABMs}{Agent Based Models}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{FFH}{Fast and Frugal Heuristic}
  \acro{OFC}{orbito-frontal cortex}
  \acro{BACCO}{Bayesian Analysis of Computer Code Outputs}
  \acro{IQR}{interquartile range}
